I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-04-19 lipics-master/Paper_noProof.tex
update

>>>>

\author{Yuke Liao}{CNRS@CREATE, Singapore}{yuke.liao@cnrsatcreate.sg}{}{}

\author{Blaise Genest}{CNRS, France \and CNRS@CREATE, Singapore \and https://perso.crans.org/genest/}{blaise.genest@cnrsatcreate.sg}{}{}

\author{Kuldeep Meel}{University of Toronto, Canada \and https://www.cs.toronto.edu/~meel/}{ meel@cs.toronto.edu}{}{}

\author{Shaan Aryaman}{NYU Courant Institute of Mathematical Sciences, United States}{aryaman.shaan@gmail.com}{}{}

%\author{John Q. Public}{Dummy University Computing Laboratory, [optional: Address], Country \and My second affiliation, Country \and \url{http://www.myhomepage.edu} }{johnqpublic@dummyuni.org}{https://orcid.org/0000-0002-1825-0097}{(Optional) author-specific funding acknowledgements}
